Out-of-Sample Comparisons of Overfit Models

### 2014-02-19 paper.tex
Fix extra parenthesis in caption
Begin to rewrite assumptions

We assume the next conditions hold throughout the paper.  The first
assumption controls the dependence of the underlying random array.
The second prevents the sequence of experiments from becoming
degenerate as $T$ increases.  The third assumption controls the
smoothness of the loss function and bounds the moments of the
difference in the models' performance; the fourth assumption describes
the behavior of the estimation and test windows.  And the last
assumption describes the kernel used to estimate the \oos\ average's
asymptotic variance.

\begin{asmp}\label{asmp-1}
  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
  greater than two and discussed further in Assumption \ref{asmp-3}.
  Also, $K_1$ and $K_2$ are less than $R$, and $K_2/T$ and
  $(K_2-K_0)/T$ are uniformly positive; $K_0$ is the number of
  regressors shared by the two models ($K_1/T$ can be uniformly
  positive as well, but is not required to be).
\end{asmp}

The first assumption is a standard condition on the dependence of the
underlying stochastic array.  We assume that the array is absolutely
regular instead of strong mixing, which is more common in
econometrics, because absolute regularity admits a particular coupling
argument \citep[reproduced in this paper as Lemma A.1]{Ber:79} that is
unavailable for strong mixing sequences.  Please see, for example,
\citet{Dav:94} for a discussion of these mixing conditions.

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.
  Moreover,
  \begin{align*}
    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
  \end{align*}
  for large enough $T$, where $S = R,T$, $i = 1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
  Additionally, the Euclidean norms of the pseudo-true coefficients,
  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
  $|\theta_2|_2 = O(1)$.
\end{asmp}

@@

We can see that these conditions are trivially satisfied when the
underlying series are i.i.d.\ Normal and the regression includes a
constant.
\begin{example}
  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
  uniformly positive definite, then
  \begin{equation*}
    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
  \end{equation*}
  and the regression constant is
  \begin{equation*}
    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
  \end{equation*}
  where both of these terms follow directly from the normality
  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
  N(0, v^2)$ (independent of $x_t$) with
  \begin{equation*}
    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
  \end{equation*}
  Then we have
  \begin{equation*}
    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
    = v^2 X_{T}'X_{T}
  \end{equation*}
  and
  \begin{equation*}
    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
    \,\Big|\, X_{R}'X_{R} \Big)\Big) = P v^2 \E x_t x_t'.
  \end{equation*}

@@

\begin{figure}
  \centering {\large Simulated Rejection Probability of $F$-test Under
    $\E_T \oosB \leq 0$}
  \input{mc/plots/ftest-001.tikz}
  \caption{Simulated rejection probabilities for the $F$-test given
    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
    10\% indicate that the test rejects the benchmark model too often.
    See Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ftest}
\end{figure}
\clearpage
\begin{figure}
  \centering {\large Simulated Rejection Probability of DMW Test Under
    $\E_T \oosB \leq 0$)} \input{mc/plots/size-dmwsize.tikz}
  \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
    \protect\textsc{oos} $t$-test given $\E_T \oosB \leq 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}

>>>>

The next conditions are assumed to hold throughout the paper.  The first
assumption controls the dependence of the underlying random array.
The second layes out the details of our asymptotic approximation.
The third assumption controls the
smoothness of the loss function and bounds the moments of the
difference in the models' performance; the fourth assumption describes
the behavior of the estimation and test windows.  And the last
assumption describes the kernel used to estimate the \oos\ average's
asymptotic variance.

\begin{asmp}\label{asmp-1}
  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
  greater than two and discussed further in Assumption \ref{asmp-3}.
\end{asmp}

This assumption is a standard condition on the dependence of the
underlying stochastic array. The only novelty is that we use
absolute regularity instead of strong or uniform mixing as our
weak dependence condition; absolute regularity admits a paricular
coupling argument, ``Berbee's Lemma'' \citep[reproduced in this
paper as Lemma A.1 for reference]{Ber:79} that is
unavailable for strong mixing sequences; absolute regularity
implies uniform mixing, so this assumption is not unduly strong.
For a detailed discussion of these weak dependence conditions,
please see, for example, \citet{Dav:94}.

Our strict stationarity assumption is also somewhat stronger than is
typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
present results assuming covariance stationarity of the loss
associated with the pseudo-true models. We need to make a stronger
assumption because we will need to prove asymptotic results where the
$\bh{it}$ remain random---so we would need covariance stationarity to
hold for almost all estimates of $\theta_i$, and not just for the
pseudo-true value.

The next assumption describes our asymptotic experiment.
\begin{asmp}\label{asmp-2}
  The number of regressors for each model, $K_1$ and $K_2$, are less
  than $R$, and $K_2/T$ and $(K_2-K_0)/T$ are uniformly positive;
  $K_0$ is the number of regressors shared by the two models ($K_1/T$
  can be uniformly positive as well, but is not required to be).

  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.
  Moreover,
  \begin{align*}
    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
  \end{align*}
  for large enough $T$, where $S = R,T$, $i = 1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]

  Additionally, the Euclidean norms of the pseudo-true coefficients,
  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
  $|\theta_2|_2 = O(1)$.
\end{asmp}

@@

We can see that these conditions are trivially satisfied when the
underlying series are i.i.d.\ Normal and the regression includes a
constant.
\begin{example}
  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
  uniformly positive definite, then
  \begin{equation*}
    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
  \end{equation*}
  and the regression constant is
  \begin{equation*}
    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
  \end{equation*}
  where both of these terms follow directly from the normality
  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
  N(0, v^2)$ (independent of $x_t$) with
  \begin{equation*}
    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
  \end{equation*}
  Then we have
  \begin{equation*}
    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
    = v^2 X_{T}'X_{T}
  \end{equation*}
  and
  \begin{equation*}
    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
    \,\Big|\, X_{R}'X_{R} \Big) = P v^2 \E x_t x_t'.
  \end{equation*}

@@

\begin{figure}
  \centering {\large Simulated Rejection Probability of $F$-test Under
    $\E_T \oosB \leq 0$}
  \input{mc/plots/ftest-001.tikz}
  \caption{Simulated rejection probabilities for the $F$-test given
    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
    10\% indicate that the test rejects the benchmark model too often.
    See Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ftest}
\end{figure}
\clearpage
\begin{figure}
  \centering {\large Simulated Rejection Probability of DMW Test Under
    $\E_T \oosB \leq 0$} \input{mc/plots/size-dmwsize.tikz}
  \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
    \protect\textsc{oos} $t$-test given $\E_T \oosB \leq 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}
